mruby Bytecode Loader Using Bluetooth in Multi-VM Environment

### 2016-02-13 EMSOFT2016/thesis.tex
update

%
% File: thesis.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference,compsoc]{IEEEtran}
\usepackage{url}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\small\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\ttfamily},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    %lineskip=-0.5ex%
}

@@

%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM sceduler.
mruby on TECS has several problems at present.
One of the problems is low software development efficiency.
mruby on TECS only supports a strage device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
Developers should also restart an OS on a target device.
%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
These problem are a big burden on developers.

@@

{\bf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
    \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage device and also to restart an OS.
The loader supports the countinuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
In additon, synchronization of multipel tasks is also implemented.
\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

@@

\subsection{mruby Bytecode Loader Using Bluetooth}
\label{sec:mruby bytecode loader using Bluetooth}
This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
In the current system, the platform including mruby bytecodes are saved in a storage device.
Developers must rewrite the storage device every time the application programs are modified.
The OS on the target device should be also restarted.
It causes a low development efficiency to repeat that.
An mruby bytecode loader using Bluetooth makes the developers' burden decrease.
%The work that an SD card is in and out needs to be done just once in the beginning.
Developers should just once carry out the work to connect the storage device and start the OS.

mruby programs are consisted of mruby application and libraries.
mruby application is the main code, which developers should program.
mruby libraries are the codes defining the functions for application such as Ruby classes. 
The mruby bytecodes including mruby application and libraries can be sent and run.
However, it is also wasteful in terms of the size and time to send because libraries are not frequently modified. 
The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage device beforehand.
Due to this design, RiteVMs can share the mruby libraries.
In additon, a RiteVM can use the own library that other RiteVMs should not use.

%The development flow in an mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
In the proposed framework, the platform including RiteVMs and mruby library is compiled and copied in the storage device at the first.
%These are assumed not to be modified.
%The binary data transferred with Bluetooth is the bytecode of the main source.
In the host, the mruby application programs (.rb) are edited and compiled into the bytecodes (.mrb) by an mruby compiler.
The generated bytecodes are transferred from the host to the target device with Bluetooth.

@@

The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
The component is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generates the bytecode in the build description.
This generated bytecode is prepared beforehand in the storage device such as mruby libraries, and different from a bytecode transferred with Bluetooth.

@@

Second, the RiteVM reads the bytecode of mruby libraries.
mruby libraries are a set of Ruby classes such as motor class and sensor class.
For example, motor class defines methods to rotate and stop a motor.
The tMrubyBluetooth {\it cell} has two attributes as shown in Figure \ref{celltype_mrubybluetooth}: {\it mrubyFile} and {\it irep}.
The {\it mrubyFile} indicates the program files of mruby libraries.
{\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyFile}, does not consume memory.
The {\it irep} is the pointer of the array stored the bytecode of mruby libraries.
In short, the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.

@@

Finally, the mruby task runs.
When the mruby application is modified, only the bytecode of the modified application should be transferred.
mruby libraries need not be touched because libraries are not normally changed.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
    \caption{Control Flow of mruby bytecode loader using Bluetooth}
    \label{fig:control_flow}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tMrubyBluetooth{
    entry sTaskBody eMrubyBody;
    attr{
      [omit]char_t *mrubyFile;
      char_t *irep =
                C_EXP("&$cell_global$_irep");
    };
    var{
        uint8_t *irepApp;
    };
};
\end{lstlisting}
\caption{Celltype Description for RiteVM with mruby bytecode loader using Bluetooth}
\label{celltype_mrubybluetooth}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
void
eMrubyBody_main( CELLIDX idx )
{
  /* Declaration variables */
  mrb_state *mrb;
  mrbc_context *c;
  /* New interpreter instance */
  mrb = mrb_open();
  // Omit: error check for mrb_state
  /* New mruby context */
  c = mrbc_context_new( mrb );
  // Omit: initialization of mruby-TECS bridge
  /* Receive the bytecode via Bluetooth */
  bluetooth_loader( VAR_irepApp );
  /* Load mruby library bytecode and run */
  mrb_load_irep_cxt( mrb, ATTR_irep, c );
  /* Load mruby application bytecode and run */
  mrb_load_irep_cxt( mrb, VAR_irepApp, c );
  if ( mrb->exc ) {
    /* Failure to execute */
    mrb_p( mrb, mrb_obj_value( mrb->exc ) );
    exit( 0 );
  }
  /* Free mruby context */
  mrbc_context_free( mrb, c );
  /* Free interpreter instance */
  mrb_close( mrb );
}

@@

A RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
{\it rotateReadyQueue} is described as follows.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.pdf}
    \caption{rotateReadyQueue}
    \label{fig:rotateReadyQueue}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/Eventflag.pdf}
    \caption{The design for Eventflag using TECS}
    \label{fig:Eventflag}
\end{figure}

@@

\section{Experimental Evaluation}
\label{sec:Evaluation}
This section mentions experimental results and their consideration.
To analyze the advantages of the proposed framework, the evaluations are performed as follows.
\begin{itemize}
    \item Size and time for transferred mruby bytecodes
    \item Execution time with singletasking, co-routine, and multitasking
    \item Overhead for cyclic time
    \item Code size using the benefit of CBD 
\end{itemize}

@@

The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
The bytecode of mruby application is smaler and faster than that of including mruby libraries in all terms.
In the proposed framework, developers send only mruby application and prepare mruby library in advance.
Therefore, the design can send the bytecode faster.
In addition, the design can save the time to connect a storage device to restart an OS.
These advantages lead improvement of the software development efficiency.

@@

CodeSize

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|ccccccc}
        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & VM Managenment & VM Scheduler & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark & $\triangle$&            & \checkmark \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparison}
\end{table*}
The open-source run-time systems for scripting languages have been proposed such as follow:
python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

@@

Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.

\section{Conclusion}
\label{sec:Conclusion}
This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
The loader provides developers with the software development efficiency without rewriting a storage device and restarting an OS.
The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
The loader can improve the software development efficiency on mruby on TECS.
The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.

>>>>

%
% File: thesis.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass[conference,compsoc]{IEEEtran}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\small\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    %lineskip=-0.5ex%
}

@@

%This paper proposes two additional features of mruby on TECS, mruby bytecode loader using Bluetooth and RiteVM sceduler.
mruby on TECS has several problems at present.
One of the problems is low software development efficiency.
mruby on TECS only supports a storage/ROM device in the platform for LEGO MINDSTORMS EV3 \cite{par:EV3} to load mruby programs.
For example, an SD card should be inserted and pulled out repeatedly, or a ROM should be rewritten if mruby programs are modified.
Developers should also restart an OS on a target device.
%Moreover, in the current system if developers attempt to run multiple tasks with the same priority, a task with first execution only runs and all other tasks do not run unless developers call the OS's function.
%In addition developers must prepare as many VMs as the number of tasks because one RiteVM supports only one task.
Moreover, although mruby on TECS has supported the multi-VM, developers need to call OS's function in order to execute multiple tasks.
These problem are a big burden on developers.

@@

{\bf Contribution}: The proposed framework gives the contribution in the following points.
\begin{enumerate}
    \item {\bf To improve the software development efficiency:} Developers do not need to rewrite a storage/ROM device and also to restart an OS.
The loader supports the countinuous loading, which saves the Bluetooth set-up time.
Therefore, the mruby bytecode loader using Bluetooth helps developers develop software.
\item {\bf To effectively execute multiple mruby programs in concurrent or/and parallel:} Developers can execute multiple tasks without the knowledge of an RTOS because the RiteVM sceduler switches tasks cyclically.
In additon, synchronization of multipel tasks is also implemented.
\item {\bf To focus on the benefits of component-based developments:} This paper shows the specific examples for the benefits of component-based development. 
\end{enumerate}

@@

\subsection{mruby Bytecode Loader Using Bluetooth}
\label{sec:mruby bytecode loader using Bluetooth}
This section describes an additional functionality of mruby on TECS, mruby bytecode loader using Bluetooth.
In the current system, the platform including mruby bytecodes are saved in a storage/ROM device.
Developers must rewrite the storage/ROM device every time the application programs are modified.
The OS on the target device should be also restarted.
It causes a low development efficiency to repeat that.
An mruby bytecode loader using Bluetooth makes the developers' burden decrease.
%The work that an SD card is in and out needs to be done just once in the beginning.
Developers should just once carry out the work to connect the storage/ROM device and start the OS.

mruby programs are consisted of mruby application and libraries.
mruby application is the main code, which developers should program.
mruby libraries are the codes defining the functions for application such as Ruby classes. 
The mruby bytecodes including mruby application and libraries can be sent and run.
However, it is also wasteful in terms of the size and time to send because libraries are not frequently modified. 
The proposed framework provides the design that only mruby applications are sent and mruby libraries are preserved with the platform in the storage/ROM device beforehand.
Due to this design, RiteVMs can share the mruby libraries.
In additon, a RiteVM can use the own library that other RiteVMs should not use.

%The development flow in an mruby bytecode loader using Bluetooth is shown in Figure \ref{fig:bluetooth_loader}.
In the proposed framework, the platform including RiteVMs and mruby library is compiled and copied in the storage/ROM device at the first.
%These are assumed not to be modified.
%The binary data transferred with Bluetooth is the bytecode of the main source.
In the host, the mruby application programs (.rb) are edited and compiled into the bytecodes (.mrb) by an mruby compiler.
The generated bytecodes are transferred from the host to the target device with Bluetooth.

@@

The proposed framework provides a RiteVM with mruby bytecode loader using Bluetooth as TECS component.
The component is an extension of the RiteVM component, which is described in \cite{par:mrubyonTECS}.
The component plays a role in receiving bytecodes via Bluetooth, and also manages a RiteVM configuration such as automatically generates the bytecode in the build description.
This generated bytecode is prepared beforehand in the storage/ROM device such as mruby libraries, and different from a bytecode transferred with Bluetooth.

@@

Second, the RiteVM reads the bytecode of mruby libraries.
mruby libraries are a set of Ruby classes such as motor class and sensor class.
For example, motor class defines methods to rotate and stop a motor.
The tMrubyBluetooth {\it cell} has attributes as shown in Figure \ref{celltype_mrubybluetooth}.
The {\it mrubyFile} indicates the program files of mruby libraries.
{\it [omit]} is only used for the TECS generator, thus the attribute, {\it mrubyFile}, does not consume memory.
The {\it irep} is the pointer of the array stored the bytecode of mruby libraries.
In short, the bytecode of mruby libraries is stored as an attribute of the component when compiling for the first time.

@@

Finally, the mruby task runs.
When the mruby application is modified, only the bytecode of the modified application should be transferred.
mruby libraries need not be touched because libraries are not normally changed.
\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/control_flow.pdf}
    \caption{Control Flow of mruby bytecode loader using Bluetooth}
    \label{fig:control_flow}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tMrubyBluetooth{
    entry sTaskBody eMrubyBody;
    attr{
      [omit]char_t *mrubyFile;
      char_t *irep = C_EXP("&$cell_global$_irep");
      uint32_t irepAppSize = C_EXP( BUFFER_SIZE );
    };
    var{
        [size_is(irepAppSize)] uint8_t *irepApp;
    };
};
\end{lstlisting}
\caption{Celltype Description for RiteVM with mruby bytecode loader using Bluetooth}
\label{celltype_mrubybluetooth}
\end{figure}
\begin{figure}[t]
\centering
\begin{lstlisting}
void
eMrubyBody_main( CELLIDX idx )
{
  /* Declaration variables */
  mrb_state *mrb;
  mrbc_context *c;
  /* New interpreter instance */
  mrb = mrb_open();
  // Omit: error check for mrb_state
  /* New mruby context */
  c = mrbc_context_new( mrb );
  // Omit: initialization of mruby-TECS bridge
  /* Receive the bytecode via Bluetooth */
  bluetooth_loader( VAR_irepApp );
  /* Load mruby library bytecode and run */
  mrb_load_irep_cxt( mrb, ATTR_irep, c );
  /* Load mruby application bytecode and run */
  mrb_load_irep_cxt( mrb, VAR_irepApp, c );
  if ( mrb->exc ) {
    /* Failure to execute */
    mrb_p( mrb, mrb_obj_value( mrb->exc ) );
    exit( 0 );
  }
  /* Free mruby context */
  mrbc_context_free( mrb, c );
  /* Free interpreter instance */
  mrb_close( mrb );
}

@@

A RiteVM scheduler is a cyclic handler, and calls {\it rotateReadyQueue}, a service call of $\mu$ITRON to switch tasks with the same priority.
In other words, the RiteVM scheduler calls {\it rotateReadyQueue} cyclically.
The design of the RiteVM scheduler is shown in Figure \ref{fig:rotateReadyQueue}. 
{\it rotateReadyQueue} is described as follows.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/rotateReadyQueue.pdf}
    \caption{The design of RiteVM sceduler}
    \label{fig:rotateReadyQueue}
\end{figure}

@@

In addtion, the end of mruby applications is synchronized to accept the continuous loading.
The ending synchronization prevents a RiteVM whose application immediately finishes from waiting the next loading.
All of mruby applications finish at the same time, and all RiteVMs wait for receiving the next mruby application bytecodes.

\begin{figure}[t]
    \centering
    \includegraphics[width=8cm,clip]{figure/Eventflag.pdf}
    \caption{The design for Eventflag using TECS {\scriptsize *only differences}}
    \label{fig:Eventflag}
\end{figure}

@@

\section{Experimental Evaluation}
\label{sec:Evaluation}
This section mentions experimental results and their consideration.
To analyze the advantages of the proposed framework, the evaluations are performed as follows.
\begin{itemize}
%    \item Execution time of the platform
    \item Size and time for transferred mruby bytecodes
    \item Execution time with singletasking, co-routine, and multitasking
    \item Overhead for cyclic time
%    \item Synchronization of mruby applications
    \item Code size using the benefit of CBD 
\end{itemize}

@@

The size, load process time, and compilation time for mruby application and mruby application including library is shown in Table \ref{tab:size_and_time}.
The overhead of load processing is 50.933 msec, which it takes to load a zero bytes bytecode.
Similarly, the overhead of compilation is 46.9 msec, which it takes to compile a zero bytes program.
The mruby application bytecode is smaler and faster than that of including mruby libraries in all terms.
The difference becomes larger as the number of RiteVMs increases because it takes the 50 msec overhead per one RiteVM. 
%In the proposed framework, developers send only mruby application and prepare mruby library in advance.
%Therefore, the design can send the bytecode faster.
In addition, the design can save the time to connect a storage/ROM device to restart an OS.
These advantages lead improvement of the software development efficiency.

@@

To indicate the superior of component-based development, the comparison of code lines between two .c files is shown in Table \ref{tab:codesize}.
(A) and (B) mean the source files in the upper and lower of Figure \ref{fig:Eventflag}, respectively. 
In terms of .c, (B)'s lines do not increase even if the number of RiteVMs increases, while (A)'s lines increase in proportion to the number.
(B) is not modified, and can be utilized regardless of the number of RiteVMs.
Moreover, lines of two .cdl files are equal.
The skillfull component-based development brings this advantage such as the decrease of code lines, which leads high productivity and high maintainability.

\begin{table}[t]
    \centering
    \caption{Lines of .c and .cdl file for the number of RiteVM}
    \begin{tabular}{c||cc|c}
                & (A)       & (B)     & Diff  \\ \hline
        .c      & 134$+$8$\times$$\alpha $  & 130     & 4$+$8$\times$$\alpha$ \\
        .cdl    & 25$+$18$\times$$\alpha$   & 25$+$18$\times$$\alpha$ & 0     \\
        \multicolumn{3}{l}{  }\\
        \multicolumn{3}{l}{{\small $\alpha$} : {\scriptsize the number of RiteVM}}
    \end{tabular}
    \label{tab:codesize}
\end{table}

@@

\begin{table*}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \begin{tabular}{c||c|ccccccc}
        & Bluetooth Loader & \shortstack{Call\\C Function} & \shortstack{Legacy Code of\\Embedded System} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization of\\Application} & Co-routine \\ \hline
        python-on-a-chip \cite{url:python-on-a-chip} &            &            &            &            &             &            & \checkmark \\
        Owl system \cite{par:owl}                    &            & \checkmark & Partially  &            &             &            & \checkmark \\
        eLua \cite{url:eLua}                         &            & \checkmark & Partially  &            &             &            & \checkmark \\
        mruby \cite{par:mruby}                       &            & \checkmark &            &            &             &            & \checkmark \\
        mruby on TECS \cite{par:mrubyonTECS}         &            & \checkmark & \checkmark & \checkmark &             &            & \checkmark \\
        Proposed framework                           & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark  & \checkmark & \checkmark \\
    \end{tabular}
    \label{tab:comparison}
\end{table*}
The open-source run-time systems for scripting languages have been proposed such as follow:
python-on-a-chip \cite{url:python-on-a-chip}, the Owl system \cite{par:owl}, eLua \cite{url:eLua}, mruby \cite{par:mruby}, \cite{url:mruby}, and mruby on TECS \cite{par:mrubyonTECS}.

@@

Table \ref{tab:comparison} shows a comparison between the proposed framework and previous work.
The proposed framework supports the loader, the VM scheuler, and synchronization of application.

\section{Conclusion}
\label{sec:Conclusion}
This paper has presented an extended framework of mruby on TECS: mruby bytecode loader using Bluetooth and RiteVM scheuler.
The loader provides developers with the software development efficiency without rewriting a storage/ROM device and restarting an OS.
The proposed framework can be applied to many kinds of embedded systems  because the loader can use not only Bluetooth also wired serial connection.
%Thus, the proposed framework can be utilized on the deveces without Bluetooth.
The RiteVM scheuler makes multitasking more easily than the current mruby on TECS.
In the evaluation, experimental results of the loader and the RiteVM scheduler show their advantages.
The loader can improve the software development efficiency on mruby on TECS.
The RiteVM sceduler has the effectiveness in terms of execution time and ease of use compared with singletasking and co-routine because of the low overhead.

### 2016-02-13 abstract/abstract.tex
update

現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
さらに，マルチVMを提供しているが，複数のmrubyアプリケーションを効率よく並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．

@@

mruby on TECSでは，mrubyプログラムを修正する度にターゲットデバイスでSDカードを抜き差しし，OSを再起動する必要がある.
さらに，複数のmrubyアプリケーションを並行実行させる場合，開発者がタスクを待ち状態へ遷移させるOSの機能を呼び出さなければならない.
　
\section{提案フレームワーク}
提案フレームワークは，mruby on TECSを拡張して，Bluetoothを用いたmrubyバイトコードローダと，実用的なマルチタスク処理の実装を行った.
システムモデルを図\ref{fig:system_model}に示す.
\begin{figure}[h]
    \centering
    \includegraphics[width=7cm,clip]{Abst_SystemModel.pdf}
    \caption{System Model}
    \label{fig:system_model}
\end{figure}

@@

\begin{table}[t]
    \centering
    \caption{Comparion of the proposed and previous work}
    \scriptsize
    \begin{tabular}{c||c|c|c|c}
        & \shortstack{Bluetooth\\Loader} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization\\of Application} \\ \hline
        eLua                &            &            & &           \\
        Owl system          &            &            & &           \\
        mruby on TECS       &            & \checkmark & &           \\
        Proposed framework  & \checkmark & \checkmark & \checkmark &\checkmark \\
    \end{tabular}
    \label{tab:comparison}
\end{table}

>>>>

現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
さらに，マルチVMを提供しているが，複数のmrubyアプリケーションを効率良く並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．

@@

mruby on TECSでは，mrubyプログラムを修正する度にターゲットデバイスでSDカードを抜き差しし，OSを再起動する必要がある.
さらに，複数のmrubyアプリケーションを並行実行させる場合，開発者がタスクを待ち状態へ遷移させるOSの機能を呼び出さなければならない.
　
\section{提案フレームワーク}
提案フレームワークは，mruby on TECSを拡張して，Bluetoothを用いたmrubyバイトコードローダと，実用的なマルチタスク処理の実装を行った.
システムモデルを図\ref{fig:system_model}に示す.
\begin{figure}[h]
    \centering
    \includegraphics[width=7cm,clip]{Abst_SystemModel.pdf}
    \caption{システムモデル}
    \label{fig:system_model}
\end{figure}

@@

\begin{table}[t]
    \centering
    \caption{関連研究}
    \scriptsize
    {\tabcolsep=0.1cm
    \begin{tabular}{c||c|c|c|c}
        & \shortstack{Bluetooth\\Loader} & \shortstack{VM\\Managenment} & \shortstack{VM\\Scheduler} & \shortstack{Synchronization\\of Application} \\ \hline
        eLua                &            &            & &           \\
        Owl system          &            &            & &           \\
        mruby on TECS       &            & \checkmark & &           \\
        Proposed framework  & \checkmark & \checkmark & \checkmark &\checkmark \\
    \end{tabular}
    }
    \label{tab:comparison}
\end{table}
